\documentclass{article}
\usepackage[tut]{omegat}

\title{Combinatorics: Arranging Identical Elements}
\author{Omega Tong}
\pagestyle{fancy}
\fancyhf{}
\cfoot{\thepage}
\fancyhead[C]{Name:\qquad\qquad \qquad\qquad\\
Class:\qquad \qquad }
\fancyhead[R]{Score: \qquad/20\\
Time:\quad\ 2 hour}
\fancyhead[L]{S.3 Quiz 2\\\begin{FirstBigRestSmallCaps}
        Omega Tong
\end{FirstBigRestSmallCaps}, 21/01/2021}
\setlength{\headheight}{25pt}
\date{\today}
\def\myFBRSC#1{{\larger[0]{\MakeTextUppercase{#1}}}\scshape }
\DeclareRobustCommand{\FirstBigRestSmallCaps}[1]{\myFBRSC #1}

\begin{document}

\begin{center}
    \fbox{\fbox{\parbox{5.5in}{\centering
    Answer the questions in the spaces provided. If you run out of room for an answer, continue on the back of the page.}}}
\end{center}

\nbf{Answers:}

\begin{tabular}{|l|l|l|l|}
    \hline
    1.&\phantom{\qquad\qquad}&2.&\phantom{\qquad\qquad}\\
    \hline
\end{tabular}

\nbf{Questions:}

\begin{mysubsection}{}
    \qitem{%
        Find the last three digits non zero of $2021!$.
        }{%
        https://artofproblemsolving.com/community/c4t177f4h2413889_expression_of_2021
        }{%
        <++>
    }

    \qitem{%
        Find all $n, k, \in \mathbb{N}$ such that $n!+8=2^k$.
        }{%
        https://artofproblemsolving.com/community/c4t177f4h2415900_a_number_theory_problem
        }{%
        <++>
    }

    \qitem{%
        Find the least n such that whenever the elements of the set 1,2,....n are colored red or blue, there always exists x, y, z, w (not necessarily distinct) of the same color such that x+y+z=w.
        I solved this by taking n=1,2,3 till 11 and finally got the answer to be 11. But is there some trick or a way I can use rather than this 'brute-force' method?
        }{%
        <++>
        }{%
        https://artofproblemsolving.com/community/c4t309f4h2415308_a_counting_problem
    }

    \qitem{%
        What is the number of ways in which one can color the squares of a $4\times 4$ chessboard with colors red and blue such that each row as well as each column has exactly two red squares and two blue squares?
        }{%
        <++>
        }{%
        https://artofproblemsolving.com/community/c4t309f4h1694113_lets_do_some_combinatorics
    }

    <++>
\end{mysubsection}

\begin{enumerate}
    \item
        In $\triangle ABC$, the ratio of the altitudes perpendicular to the three sides $AB,BC$ and $CA$ is $3:4:5$. If the lengths of the three sides are integers, find the minimum value of $AB$.
    \item
        Find the value of $\sqrt{7-\sqrt{12}-\sqrt{13-2\sqrt{12}}}$.
    \item
        In Figure 2,  $ABCD$ is a trapezium with $\angle C=90$. If the area of the equilateral triangle  $ABD$  is $16\sqrt{3}$, find the area of trapezium $ABCD$.
    \item
        Given that  $a,b$ and $c$ are integers, and $a + b = 2011$, $c-a = 2010,  a < b$. Find the greatest possible value of $a + b + c$.
    \item
        Given that $f(x)=\frac{4^{x}}{4^{x}+2}$, where $x$ is a real number, find the value of\\
        $f(\frac{1}{2011})+f(\frac{2}{2011})+\cdots+f(\frac{2010}{2011})$.
    \item
        In numbering the pages of a magazine, $2,046$ digits were used. How many pages are there in the magazine? (Assume the page number of the magazine starts from $1$.)
    \item
        As shown in Figure 1, $P$ is a point inside a rectangle $ABCD$ such that $PA = 2$, $PB = 3$ and $PC = 5$. Find the length of $PD$.
    \item
        As  shown  in  Figure  2,  two  squares  with  side  $x$  cm  coincides  at  one  corner.  If  the  ratio  of  the  non-overlapping area to the overlapping area of the two squares is $a : 1$, find the value of $a$.
    \item
        Given that  $a ,  b ,  c ,  d ,  e ,  f ,  g$  and  $h$  are positive integers such that $a>b>c>d>e>f>g>h$ and $a+h=b+g=c+f=d+e=35$. How many possible solution set of $\left\{a,b,c,d,e,f,g,h\right\}$ exist?
    \item
        Find the value of $\left(\frac{1}{2}+\frac{1}{3}+\cdots+\frac{1}{100}\right)+\left(\frac{2}{3}+\frac{2}{4}+\cdots+\frac{2}{100}\right)+\left(\frac{3}{4}+\frac{3}{5}+\cdots+\frac{3}{100}\right)+\cdots+\left(\frac{98}{99}+\frac{98}{100}\right)+\frac{99}{100}$.
\end{enumerate}
\begin{enumerate}
    \item In the following figure, $ABCDEF$ is a regular hexagon centered at the point $P$. $\triangle PST$ is an equilateral triangle. It is given that $AB=6$ cm, $QD=2$ cm and $PT=12$ cm. If the area of the common part of the hexagon and triangle is $c$ cm$^2$, find the value of $c$.
    \item Let $x=1+\sqrt{2}$, find the value of $x^{5}-2x^{4}+3x^{3}-4x^{2}-10x-6$.
    \item In the following figure, $ABCD$ is a square and $AM=NB=DE=FC=1$ cm and $MN=2$ cm. Let the area of quadrilateral $PQRS$ be $c$ cm$^2$, find the value of $c$.
    \item In the following figure, $\angle ACB$ is a right angle, $AC=BC=14$ cm and $CE=CF=6$ cm. If $CD=d$ cm, find the value of $d$.
    \item Let $x$ be a positive real number. Find the minimum value of $\displaystyle x^{2008}-x^{1004}+\frac{1}{x^{1004}}$.
    \item Let $x$ and $y$ be real numbers satisfying
        \begin{equation*}
            \begin{cases}
                \left(x-\frac{1}{3}\right)^{3}+2008\left(x-\frac{1}{3}\right)=-5,\\
                \left(y-\frac{7}{4}\right)^{3}+2008\left(y-\frac{7}{4}\right)=5.
            \end{cases}
        \end{equation*}
        If $z=x+y$, find the value of $z$.
    \item Given that $k$, $x_{1}$ and $x_{2}$ are positive integers with $x_{1}<x_{2}$. Let $A,B$ and $C$ be three points on the curve $y=kx^2$, with $x$ coordinates being $-x_{1}$, $x_{1}$ and $x_{2}$ respectively. If the area of $\triangle ABC$ is 15 sqare unites, find the sum of all possible values of $k$.
    \item In the following figure, $ABCD$ is a rectangular piece of paper with $AB=4$ cm and $BC=5$ cm. Fold the paper by putting point $C$ onto $A$ to create a crease $EF$. If $EF=r$ cm, find the value of r.
    \item A game show offers a contestant three prizes A, B and C, each of which is worth a whole number of dollars from $\$ 1$ to $\$ 9999$ inclusive. The contestant wins the prizes by correctly guessing the price of each prize in the order A, B, C. As a hint, the digits of the three prices are given. On a particular day, the digits given were $1,1,1,1,3,3,3$. Find the total number of possible guesses for all three prizes consistent with the hint.
    \item For $t=1,2,3,4$, define $\displaystyle S_{t}=\sum_{i=1}^{350}a_i^t$, where $a_i\in \left\{1,2,3,4\right\}$. If $S_1=513$ and $S_4=4745$, find the minimum possible value of $S_{2}$.
\end{enumerate}

\end{document}
