\pitem[Brazil Cono Sur TST 2021 P2]{%
There are $2022$ cards inside a box. Each of them has two-sided cards: one black and one white.
Ana and Beto play the following game: Ana puts the $2022$ cards in a row (on some of the cards the top face
will be black and in others the top face will be white). After that, Beto can perform moves, no more than
that $2022$ times: he chooses a card, turning it over and turning his neighbor(s) card(s) (if he draws a
top face is black, it flips to white face and vice versa). Beto wins the game if he gets all the
cards are white-faced, otherwise Ana wins the game. Someone has a winning strategy?
Note: The cards at the beginning and end of the row have $1$ neighboring cards and the other cards have $2$
neighboring cards.
    }{%
    We will show that Beto has the winning strategy.
First of all ignore the condition that he can make at most $2022$ moves. We will allow an arbitrary number of moves, and then if we applied $k$ moves on a certain location, we replace $k$ with $k \pmod 2$ and become safe.
The main portion of the proof that follows hinges on $2022 \equiv 0 \pmod 3$. Now we run a linear scan on all indices from left to right. (let us number them from $1$ to $2022$ for convenience)
If the current card is colored White, just pass through it, otherwise flip the card next to it. (we stop when we reach the last card, and do not apply this move there)
This ensures that the first $2021$ cards are White. If the last one is also white, we are done. So assume that it is Black. If we apply the given type of on consecutive cards, then we immediately notice that we can swap indices $i$ and $i+3$ at the same time. Inductively, this also yields that it is possible to swap $i$ and $j$ with $i \equiv j \pmod 3$ without affecting rest of the board. In particular we can do this on $3$ and $2022$. So now location $3$ is black, all others are white. Apply the move on location $2$ and then location $1$. This completes the algorithm.
    }{%
    https://artofproblemsolving.com/community/c6t224166f6h2638921_black_and_white_cards_game
}
