\pitem[SAMO 2017 Q4]{%
    Andile and Zandre play a game on a $2017 \times 2017$ board. At the beginning, Andile declares some of the squares forbidden, meaning the nothing may be placed on such a square. After that, they take turns to place coins on the board, with Zandre placing the first coin. It is not allowed to place a coin on a forbidden square or in the same row or column where another coin has already been placed. The player who places the last coin wins the game.  
    What is the least number of squares Andile needs to declare as forbidden at the beginning to ensure a win? (Assume that both players use an optimal strategy.)
    }{%
    The answer is $2017$. For $2017$, Andile can just declare an entire row forbidden. Now there are $2016$ rows and $2017$ columns, and each move will reduce the number of available rows and columns each by $1$. As there are more columns than rows, the game ends when we run out of rows. Since $2016$ is even, Andile wins.

    Now we show that $2016$ is not enough. We will prove the following statement by induction.

    \textbf{Claim:} On a $(2n+1)\times(2n+1)$ board, if at most $2n$ squares are forbidden then Zandre wins.

    \textbf{Proof:} The base case $n=0$ is trivial.
    Now suppose we have a $(2k+1)\times (2k+1)$ board with at most $2k$ forbidden squares $(k\geq 1)$.

    \begin{itemize}
        \item If there are at most one forbidden square, Zandre chooses some other square in its row. Now whatever square Andile chooses, we're left with $0$ forbidden squares on a $(2k-1)\times(2k-1)$ board.
        \item Else there are at least 2 forbidden squares.
            If some two of them are in the same row or column, Zandre chooses a non-forbidden square in that row or column (which exists since $2k<2k+1$).
        \item 
            Else consider two forbidden squares $X,Y$. Zandre choose the square $Z$ on the same row as $X$ and same column as $Y$.
            Now whatever square Andile chooses, we're left with at most $2k-2$ forbidden squares on a $(2k-1)\times(2k-1)$ board. $\square$
    \end{itemize}
    Hence Andile needs at least $2017$ forbidden squares.
    }{%
    https://artofproblemsolving.com/community/c6t45487f6h1486763_game_involving_placing_coins_on_a_chessboard
}
