\pitem[2021 Dutch BxMO TST p4]{%
    Jesse and Tjeerd are playing a game. Jesse has access to $n\ge 2$ stones. There are two boxes: in the black box there is room for half of the stones (rounded down) and in the white box there is room for half of the stones (rounded up). Jesse and Tjeerd take turns, with Jesse starting. Jesse grabs in his turn, always one new stone, writes a positive real number on the stone and places put him in one of the boxes that isn't full yet. Tjeerd sees all these numbers on the stones in the boxes and on his turn may move any stone from one box to the other box if it is not yet full, but he may also choose to do nothing. The game stops when both boxes are full. If then the total value of the stones in the black box is greater than the total value of the stones in the white box, Jesse wins; otherwise win Tjeerd. For every $n \ge  2$, determine who can definitely win (and give a corresponding winning strategy).
    }{%
    We claim that $\boxed{\text{Jesse}}$ can always win.
Let Jesse place $2^0 = 1$ in the black box. In each of his moves, Jesse either places the number half the smallest power of two, or the number twice the largest power of two which he has already placed. For example, if Jesse has already placed $2^{-i}, 2^{-i+1},\dots,2^{-1}, 2^0, 2^1, \dots, 2^{j-1}, 2^j$, then he could either place $2^{-i-1}$ or $2^{j+1}$ on his next turn. The box in which Jesse would place his number depends on Tjeerd's actions.

The goal of Jesse is to keep the largest power of $2$ is the black box after his turn. If Tjeerd transfers the largest power of $2$ to the white box, then Jesse places the number twice of that in the black box, keeping the largest power of $2$ in the black box. If Tjeerd does nothing or transfer a power of $2$ which isn't the largest, then Jesse places the number half the smallest power of $2$ in any box available, keeping the largest power of $2$ in the black box. Note that Jesse has the final move, so at the end of the game the largest power of $2$ is in the black box. Since $2^{-i} + 2^{-i+1}+\dots+2^{-1}+ 2^0+ 2^1+ \dots+ 2^{j-1}< 2^j$, Jesse wins.
    }{%
    https://artofproblemsolving.com/community/c6t224166f6h2746261_2player_2_boxes_game_with_n_stones
}
