\qitem{%
    You are going to an amusement park.  There are four attractions, (haunted house, roller coaster, a carousel, water ride). You buy 25 tokens.  Each attraction cost 3 tokens each ride, except the roller coaster that costs 5. Obviously, you want to ride each ride at least once, but the order of the rides does not matter.

    In how many ways can you spend your tokens?  You may have some remaining tokens in the end of the day.
    }{%
    After riding each once, we have 11 tokens left. We can choose to go for rollar coaster 0,1, of 2 times.

    For 0 times, we have it equal to solving $3a+3b+3c\leq 11$, which equals $3(a+b+c)\leq 9$, $(a+b+c+d)=3$. Hence it is $C_{3}^{3+4-1} $.

    For 1 times, we have it equal to solving $3a+3b+3c\leq 6$, which equals $3(a+b+c)\leq 6$, $(a+b+c+d)=2$. Hence it is $C_{2}^{2+4-1} $.

    For 2 times, there is just one tocken left. So there is one solution

    Ans$=20+10+1=31$.
    }{%
    <++>
}

\qitem{%
    At an amusement park, you pay for attractions using tokens. Thereare five different attractions which cost 3 tokens each, and one attraction which cost 5 tokens.  You have 42 tokens and you want to use all of them.  How many different selections of attractions are there?
    }{%
    The questions is equivalent to solving $3x_1+3x_2+3x_3+3x_4+3x_5+5y=42$. Since we need to use all tokens, the number of times we can spend on the attraction that cost 5 tokens are $0,3,6$.

    So we are left to solve $3(x_1+x_2+x_3+x_4+x_5)=12\textnormal{ or }27\textnormal{ or }42$.

    The final answer:
    \[{4+5-1\choose 5-1}+{9+5-1\choose 5-1}+{14+5-1\choose 5-1}=3845\]
    }{%
    <++>
}

\qitem{%
    You have $2$ copies of the letter A and and unlimited supply of the letters B, C and D. How many words of length $10$ can you make from these such that all A are used, the thired letter is an A, and there is no B appearingg between the A's.
    }{%
    There are two case: there is a A before the third A or not.

    If there is no A before the first A, we have the sequence as XXAY..YAX.., where Y can be C/D and X can be B/C/D.

    Since there can be $0-6$ Y, we have a total of
    \[\sum_{k=0}^{6}2^k3^{8-k}=3^8\sum_{k=0}^{6}\left(\frac{2}{3}\right)^k=3^8\cdot \frac{1-(2/3)^7}{1-(2/3)}=3^2(3^7-2^7).\]

    And if there is a A before the third A, we have the sequence in AYAX... or XAAX..., which have $2\cdot 3^7$ and $3^8$ respectively.

    Hence there are a total of $3^9-9\cdot 2^7+2\cdot 3^7+3^8$ sequence.
    }{%
    <++>
}
