\mysection{Sticks and Balls}

\begin{shortque}[Introductory questions]{}
    \qitem{%
        $2$ candies with different flavour are distributed among $5$ students, given that a student can get at most $1$ candy. How many ways are there? \vfill
        }{%
        \begin{equation*}
            P^5_2
        \end{equation*}
        }{%
        <++>
    }

    \qitem{%
        $2$ candies with the same flavour are distributed among $5$ students, given that a student can get at most $1$ candy. How many ways are there? \vfill
        }{%
        \begin{equation*}
            C^5_2
        \end{equation*}
        }{%
        <++>
    }

    \qitem{%
        $2$ candies with different flavour are distributed among $5$ students. How many ways are there? \vfill
        }{%
        \begin{equation*}
            5^2
        \end{equation*}
        }{%
        <++>
    }

    \qitem{%
        $2$ candies with the same flavour are distributed among $5$ students. How many ways are there? \vfill
        }{%
        \begin{equation*}
            5+C^5_2
        \end{equation*}
        }{%
        <++>
    }
\end{shortque}

\begin{example}[exp:]{Concepts of Sticks and Balls}
    \eitem{%k
        Find the number of ways to put 6 identical balls into 5 different boxes.
        }{%
        We may view the question in another direction. We may consider there is a big box, and we put $5-1=4$ sticks ($|$) into the box and separate it into 5 sections. Then we further put the 6 balls ($O$) into the big box. Every configuration we have by putting sticks and balls in the big box is equivalent to one way of putting 6 balls into 5 different boxes. And every way of putting 6 balls into 5 different boxes can be represented as a sticks and balls configuration.

        Therefore, the number of ways to put 6 identical balls into 5 different boxes is equivalent to arrange 6 balls and 4 sticks. (i.e. arranging $||||OOOOOO$)

        $||OO|OO|OO$

        Number of ways $=C^{10}_4$

        2 candies to 5 student

        $C^{5+2-1}_2$
        

    }
\end{example}
\pagebreak

\begin{shortque}[]{}
    \qitem{%
        Find the number of ways of distributing 15 identical candies to 6 students, where each of them has at least 1 candy.
        }{%
        \begin{equation*}
            C^{9+5}_5
        \end{equation*}
        }{%
        <++>
    }
\end{shortque}

\begin{shortque}[Extension of sticks and balls]{}
    \qitem{%
        Find the number of ways to arrange $AABBBCCCC$.
        }{%
        <++>
        }{%
        <++>
    }

    \qitem{%
        Find the number of ways to arrange $AABBBCCCC$ without having 2 consecutive $A$s.
        }{%
        $(9!)/(2!*3!*4!)-(8!/3!/4!)$ or $(8C2 * 7!) / (3! * 4!)$

        980
        }{%
        <++>
    }

    \qitem{%
        Find the number of ways to arrange $AABBBCCCC$ without having 2 consecutive $B$s.

        \nbf{Hint: }We may consider the $B$s as sticks.
        }{%
        $(7C3) * 6!/(2!*4!)=525$
        
        }{%
        <++>
    }
    \pagebreak
\end{shortque}
